---
title: "STAT344 Final Project"
author: ''
date: "28/09/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r eval= FALSE, error = FALSE}
library(dplyr)  
library(tidyr)
library(ggplot2)  
library(magrittr) 
library(MASS)
library(readxl)
library(readxl)
```

# Import Dataset

```{r echo = TRUE}
Rooms <- read.csv("C:/Users/Melody Lo/OneDrive - UBC/Desktop/2022W/STAT344/Rooms.csv")
head(Rooms)
```

# Preliminary Study:
The parameter values from [our school website]{https://learningspaces.ubc.ca/find-space} provides that the:

* The mean learning space capacity $\mu = 62.77$
* The standard deviation $\sigma = 68.325$ 
* True proportion of learning spaces > 140 in capacity $p = 0.1094675$
* 
```{r echo = TRUE}
# Continuous Case
mean(Rooms$CAPACITY)
sd(Rooms$CAPACITY) # 68.426 or 68.325

# Binary Case
sum((Rooms$CAPACITY>=140)/338) #0.1094675
sqrt((0.1094675)*(1-0.1094675)) # 0.3122249

```
We want the width of our confidence interval in estimating average capacity size of UBC learning spaces to be less than 20. Thus:
$2\times 1.96\times \sqrt{(1-\frac{n}{338})\times\frac{68.426^2}{n}} < 20$. which gives an sample size of $n=118$. 

As for the discrete case, we look at the proportion of learning spaces with capacity larger than 140 students. We take the worst case scenario for $\hat p = 0.5$

Thus, $s^2_{guess}$ = $0.5(1-0.5)=0.25$
To receive results within $\pm0.05$, we solve for:
$0.05=1.96\times\sqrt{(1-\frac{n}{338})\times\frac{0.5^2}{n}}$ which gives **$n=180$**


# SRS Sampling
```{r echo = TRUE}
set.seed(12345)
srs <- sample(1:338, 180, replace = FALSE)
sort(srs)

```
```{r echo = TRUE}
sample<-Rooms$CAPACITY[srs]
sample
sort(sample) # Sample values for learning space capacity 
```
# Continuous
```{r echo = TRUE}
cts_mean=mean(sample) # Continuous case, mean capacity for sample = 64.167
cts_sd=sd(sample) # 74.025

```
### 95% Confidence Interval
```{r echo = TRUE}
lower_bound=cts_mean-1.96*cts_sd/sqrt(180)*sqrt(1-180/338)

upper_bound=cts_mean+1.96*cts_sd/sqrt(180)*sqrt(1-180/338)

print(c(lower_bound,upper_bound))
```
# Binary
```{r echo = TRUE}
prop<-(sum(sample>=140)/180)
prop # 0.1056
sd_prop<-(sqrt(prop*(1-prop)))
sd_prop # 0.3073
```

### 95% Confidence Interval
```{r echo = TRUE}
lower_bound_bin=prop-1.96*sd_prop/sqrt(180)*sqrt(1-180/338)

upper_bound_bin=prop+1.96*sd_prop/sqrt(180)*sqrt(1-180/338)

print(c(lower_bound_bin,upper_bound_bin))

```

# Stratified Sampling 
We will have our strats based on the type of furniture in the learning space. The possible types are the following:
* Fixed Tablets
* Fixed Tables
* Moveable Tables
* Moveable Tablets
* Mixed

```{r echo = TRUE}
library(dplyr)
mixed<-filter(Rooms,FURNITURE.TYPE=='Mixed')
fixedtablets<-filter(Rooms,FURNITURE.TYPE=='Fixed Tablets')
fixedtables<-filter(Rooms,FURNITURE.TYPE=='Fixed Tables')
moveabletablets<-filter(Rooms,FURNITURE.TYPE=='Moveable Tablets')
moveabletables<-filter(Rooms,FURNITURE.TYPE=='Moveable Tables')


```
We choose are sample size to be $\frac{nrow(...)}{338}*180$

* mixed n = 4
* fixed tablets n = 16
* fixed tables n = 46
* moveable tablets n= 18
* moveable tables n = 98

total sample size = 182


```{r echo = TRUE}

# sampling
set.seed(200)

mixed_sample<-sample_n(mixed,size=4,replace=FALSE)
fixedtablets_sample<-sample_n(fixedtablets,size=16,replace=FALSE)
fixedtables_sample<-sample_n(fixedtables,size=46,replace=FALSE)
moveabletablets_sample<-sample_n(moveabletablets,size=18,replace=FALSE)
moveabletables_sample<-sample_n(moveabletables,size=98,replace=FALSE)

stratified_sample=rbind(mixed_sample,fixedtablets_sample,fixedtables_sample,moveabletablets_sample,moveabletables_sample)

```

```{r echo = TRUE}
# standard deviaion
strata_mean=mean(stratified_sample$CAPACITY) #67.26823
strata_sd=sd(stratified_sample$CAPACITY) # 74.81512

```

### 95% Confidence Interval
```{r echo = TRUE}
lb_strata=strata_mean-1.96*strata_sd/sqrt(182)*sqrt(1-182/338)

ub_strata=strata_mean+1.96*strata_sd/sqrt(182)*sqrt(1-182/338)

print(c(lb_strata,ub_strata))
```

```{r echo = TRUE}
prop_strat<-(sum(stratified_sample$CAPACITY>=140)/182)
prop_strat # 0.1263736

sd_prop_strat<-(sqrt(prop_strat*(1-prop_strat)))
sd_prop_strat # 0.33227
```

### 95% Confidence Interval
```{r echo = TRUE}
lb_strata_p=prop_strat-1.96*sd_prop_strat/sqrt(182)*sqrt(1-182/338)

ub_strata_p=prop_strat+1.96*sd_prop_strat/sqrt(182)*sqrt(1-182/338)

print(c(lb_strata_p,ub_strata_p))

```


